No Replication Without Process Documentation:  An Assessment of Management

### 2020-05-04 R/MSE-manuscript.Rmd
Change the shape of the climate change and random sample points in MSE.map

# plot MSEs on map
MSE.map<-ggplot(data=map.data,aes(x=Longitude, y=Latitude,color=Drivers)) + world +
  geom_point(size=2.5) + geom_point(size = 2.5, colour = "gray55", shape = 1) +
  scale_color_manual(values=c("gray10","gray55"))+theme_void() +
  theme(legend.position = c(0.15, 0.25))

>>>>

# plot MSEs on map
MSE.map<-ggplot(data=map.data,aes(x=Longitude, y=Latitude,group=Drivers)) + world +
  geom_point(aes(shape=Drivers,color=Drivers,fill=Drivers),size=2.5) + 
  geom_point(aes(shape=Drivers),size = 2.5, colour = "gray45") +
  scale_shape_manual(values=c(21,22))+scale_fill_manual(values=c("gray10","gray80"))+theme_void() +
  theme(legend.position = c(0.15, 0.25))
